---
title: "R ERDDAP work"
output:
  html_document:
    df_print: paged
---

```{r}
library(rerddap)
library(tidyverse)
library(mapdata)
library(cmocean)
library(gganimate)
library(plotdap)
```

Search for data sources. Returns too many!

```{r}
ed_search("SST MODIS")
```

Check out metadata for a griddap dataset and a tabledap dataset. `browse()` pulls up a browser tab, so only works interactively.

```{r}
# browse("jplMURSST41")
# browse('siocalcofiHydroCasts')
info('jplMURSST41')
```

Set a bounding box for NES LTER in time and space.

```{r}
latitude = c(39., 42)
longitude = c(-72., -69.)
time = c("2021-11-05", "2021-11-05")
```

Grab info for MUR SST and get data for our bounding box.

```{r}
sstInfo <- info('jplMURSST41')
murSST <- griddap(sstInfo, 
                  latitude = latitude, 
                  longitude = longitude, 
                  time = time, 
                  fields = 'analysed_sst')
```

Map it! Use `map_data()` for a coast map and our MUR SST data for the raster. 
Nice scales in `cmocean`. Passing `expand = FALSE` to `coord_fixed` makes 
the raster extend to the edge of the plot.

```{r}
w <- map_data("worldHires", ylim = latitude, xlim = longitude)
ggplot(data = murSST$data, aes(x = lon, y = lat, fill = analysed_sst)) +
    geom_polygon(data = w, aes(x = long, y = lat, group = group), fill = "grey80") +
    geom_raster(interpolate = FALSE) +
    scale_fill_cmocean() +
    # scale_fill_gradientn(colours = cmocean('thermal'), na.value = NA) +
    theme_bw() + ylab("latitude") + xlab("longitude") +
    coord_fixed(1.3, xlim = longitude,  ylim = latitude, expand = FALSE) +
    ggtitle("MUR SST",
            subtitle = time[1])
```

OK, now a function to get SST for NES-LTER for a given date.
Return the latest data if no date given.

```{r}
plot_LTER_SST <- function(date = "last") {
  latitude = c(39., 42)
  longitude = c(-72., -69.)
  sstInfo <- info('jplMURSST41')
  murSST <- griddap(sstInfo, 
                    latitude = latitude, 
                    longitude = longitude, 
                    time = c(date, date), 
                    fields = 'analysed_sst')
  
  w <- map_data("worldHires", ylim = latitude, xlim = longitude)
  ggplot(data = murSST$data, aes(x = lon, y = lat, fill = analysed_sst)) +
    geom_polygon(data = w, aes(x = long, y = lat, group = group), fill = "grey80") +
    geom_raster(interpolate = FALSE) +
    scale_fill_cmocean() +
    theme_bw() + ylab("latitude") + xlab("longitude") +
    coord_fixed(1.3, xlim = longitude,  ylim = latitude, expand = FALSE) +
    ggtitle("MUR SST",
            subtitle = time)
}
```

Testing...

```{r}
plot_LTER_SST("2021-11-01")
```

Trying out the plotdap package. It's pretty much a high(er) level 
wrapper for the stuff above. plotdap can animate plots if the
data is a timeseries!

```{r}
  sstInfo <- info('jplMURSST41')
  murSST <- griddap(sstInfo, 
                    latitude = latitude, 
                    longitude = longitude, 
                    time = c("2021-11-01", "2021-11-16"), # get data for a range of dates
                    fields = 'analysed_sst')

plotdap(mapTitle = "MUR SST") %>%
    add_griddap(
      murSST, 
      ~analysed_sst, 
      time = identity,
      fill = "thermal",
      animate = TRUE
      ) %>%
    print(landmask = TRUE)
```

And now, animate across a range of dates. This is in progress....

```{r}
latitude = c(39., 42)
longitude = c(-72., -69.)
time = c("2021-11-05", "2021-11-06")

sstInfo <- info('jplMURSST41')
murSST <- griddap(sstInfo, 
                  latitude = latitude, 
                  longitude = longitude, 
                  time = time, 
                  fields = 'analysed_sst')

w <- map_data("worldHires", ylim = latitude, xlim = longitude)
p <- ggplot(data = murSST$data, aes(x = lon, y = lat, fill = analysed_sst)) +
    geom_polygon(data = w, aes(x = long, y = lat, group = group), fill = "grey80") +
    geom_raster(interpolate = FALSE) +
    scale_fill_cmocean() +
    theme_bw() + ylab("latitude") + xlab("longitude") +
    coord_fixed(1.3, xlim = longitude,  ylim = latitude, expand = FALSE) +
    ggtitle("MUR SST",
            subtitle = time[1])

p + transition_states(time)
```
