---
title: "Underway Oxygen"
author: "Brett Longworth"
date: "11/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(patchwork)
library(fuzzyjoin)
library(data.table)

# Cruise data directory
data_dir <- "/Users/brett/Documents/AR61b"

# Underway data
underway_dir <-  "data"
```

Looking at causes of supersaturation in EIMS oxygen optode. 

I suspect that supersaturation in rough weather is mostly due to aeration in the sea chest, not natural aeration due to wave action. I noticed that optode saturation peaks seemed to correspond to time on station during the 2021-11-12 OOI alongshore (AS1-AS7) CTD transect.

Get optode data

```{r}
optode_file <- file.path(data_dir, "20211112T000001.txt")

optode <- read_table(optode_file, skip = 12, 
                   col_names = FALSE) %>% 
  mutate(time = as.POSIXct(paste(X1, X2), format="%Y-%m-%d %H:%M:%S")) %>% 
  select(time, sat = X7, temp = X8, ox = X9)
```

Plot
```{r}
ggplot(optode) +
  geom_line(aes(time, sat))
```

Load ship track data

```{r}
ship_file <- file.path(underway_dir, "AR211112_0000.csv")
ship <- read_csv(ship_file, skip = 1) %>% 
  mutate(time = as.POSIXct(paste(DATE_GMT, TIME_GMT), format="%Y-%m-%d %H:%M:%S"))
  
```

Basic plot

```{r}
ggplot(ship) +
  geom_point(aes(time, HDT))
```

Combined plot

```{r}
ox <- ggplot(optode, aes(time, sat)) +
  geom_line()
hd <- ggplot(ship, aes(time, HDT)) +
  geom_line()
spd <- ggplot(ship, aes(time, SPD)) +
  geom_line()
  
ox / hd / spd
```
Join dataframes on timestamp

solution from https://stackoverflow.com/questions/65858965/is-there-an-elegent-way-to-merge-two-data-frame-by-timestamp-in-r

```{r}
optode_ship <- as.data.table(ship)[optode, on = .(time), roll = TRUE]
```

```{r}
ggplot(optode_ship, aes(WXTS_TS, sat)) +
  geom_point()
```

