---
title: "Underway Oxygen"
author: "Brett Longworth"
date: "11/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(data.table)
#library(tidymodels)
library(corrr)
library(ggplot2)
library(patchwork)

# Cruise data directory
data_dir <- "/Users/brett/Documents/AR61b"

# Underway data
underway_dir <-  "data"
```

Looking at causes of supersaturation in EIMS oxygen optode. 

I suspect that supersaturation in rough weather is mostly due to aeration in the sea chest, not natural aeration due to wave action. I noticed that optode saturation peaks seemed to correspond to time on station during the 2021-11-12 OOI alongshore (AS1-AS7) CTD transect.


Get optode and ship data

```{r}
optode_file <- file.path(data_dir, "20211112T000001.txt")
ship_file <- file.path(underway_dir, "AR211112_0000.csv")

optode <- read.table(optode_file, skip = 12, 
                   header = FALSE) |>
  data.table()
optode[, time := as.POSIXct(paste(V1, V2),  tz = "GMT")]
optode <- optode[, .(time, sat = V7, temp = V8, ox = V9)]

ship <- fread(ship_file, skip = 1)
ship[, time := as.POSIXct(paste(DATE_GMT, TIME_GMT), 
                          format="%Y/%m/%d %H:%M:%S", tz = "GMT")]
  
```

Join dataframes on timestamp

solution from https://stackoverflow.com/questions/65858965/is-there-an-elegent-way-to-merge-two-data-frame-by-timestamp-in-r

```{r}
optode_ship <- optode[ship, on = .(time), roll = TRUE]
```

Trim dataset to likely predictors

```{r}
ox_ship_trim <- optode_ship[, .(time, sat, shipsal = SBE45S,
                                shiptemp = SBE48T, FLR, FLOW, 
                                SPD, HDT, COG, SOG, 
                                air_press = WXTP_Pa,
                                rel_wind_dir = WXTP_Dm,
                                rel_wind_spd = WXTP_Sm, 
                                true_wind_spd =WXTP_TS,
                                true_wind_dir = WXTP_TD)]
```

Plot correlates

```{r}
options(digits = 1, scipen = 9999)
print(correlate(ox_ship_trim[, .SD, .SDcols = is.numeric]))
```


```{r}
plot(ox_ship_trim[, .SD, .SDcols = is.numeric])
```


Plot some potentially interesting variables vs time

There's some interesting stuff here. There may be a lag relationship in the seawater feed to changes in speed and heading. Also, saturation drops when the underway flow drops. I may have recirculated beaker water during these times to keep air out of the filter. Need to check notes.

```{r, fig.height=9}
ox <- ggplot(optode_ship, aes(time, sat)) +
  geom_line()
hd <- ggplot(optode_ship, aes(time, HDT)) +
  geom_line()
spd <- ggplot(optode_ship, aes(time, SPD)) +
  geom_line()
sog <- ggplot(optode_ship, aes(time, SOG)) +
  geom_line()
flow <- ggplot(optode_ship, aes(time, FLOW)) +
  geom_line()
  
ox / flow / hd / spd / sog
```

Polar plot of heading vs speed with saturation as color

```{r}
ggplot(ox_ship_trim, aes(HDT, SPD, color = sat)) +
  geom_point() +
  coord_polar() +
  xlim(0,360)
```

```{r}
ggplot(ox_ship_trim, aes(SPD, sat, color = true_wind_spd)) +
  geom_point() 
```

```{r}
ggplot(ox_ship_trim, aes(true_wind_dir, SPD, color = sat)) +
  geom_point() +
  coord_polar() +
  xlim(0,360)
```

```{r}
ggplot(ox_ship_trim, aes(HDT, SPD, color = sat)) +
  geom_point() +
  coord_polar() +
  xlim(0,360)
```

```{r}
ggplot(ox_ship_trim, aes(rel_wind_spd, SPD, color = sat)) +
  geom_point()
```


Linear model with speed, heading and wind speed

```{r}
sat_fit <- lm(sat ~ rel_wind_spd * true_wind_spd * HDT * SPD + FLR, data = ox_ship_trim)

summary(sat_fit)

```