---
title: "CTD Data with OCE"
format: html
editor: source
---

```{r}
library(tidyverse)
library(oce)
library(ocedata)
library(raster)
library(ncdf4)

```

```{r}
c2 <- read.ctd("data/ar70b_002.cnv")

summary(c2)
plot(c2)
```


Downloaded files to data directory...

```{r}
files <- dir("data", ".cnv$", full.names = TRUE)

ctds <- map(files, read.ctd)
```

Clean up and just look at downcast

```{r}
ctds_trimmed <- map(ctds, \(x) ctdDecimate(ctdTrim(x, method = "downcast"), p = 0.2))

```

Plot profiles

```{r}
walk(ctds, plot)
walk(ctds_trimmed, plot)
```

Make a section of mainline stations

```{r}
section <- ctds_trimmed[c(1,2,4,5,8,9,10)] |> 
  as.section()

section
```

Basic Plot

```{r}
section |> plot()
```

Interpolated plot with bathymetry

```{r}
t <- download.topo(west = -72.5, east = -69, north = 41, south = 39.5) |> 
  read.topo()

section |> 
  plot(which = c("map", "temperature", "salinity", "oxygen"), ztype = "image", showBottom = t, showStations = TRUE)
```

AR66b from DLA webserver

```{r}
base <- "https://dlacruisedata.whoi.edu/AR/cruise/AR66-B/ctd/process/"
filenames <- sprintf("ar66b%03d.cnv", 1:54)
files <- paste0(base, filenames)

outfiles <- paste0("data/", filenames)
# have to download the files first
download.file(files, outfiles)

# import the files
ctds <- map(outfiles, read.ctd)
```

```{r}
summary(ctds[[1]])
```

Clean up and just look at downcast

```{r}
ctds_trimmed <- map(ctds, \(x) ctdDecimate(ctdTrim(x, method = "downcast"), p = 0.2))
```

Plot profiles

```{r}
#walk(ctds, plot)
walk(ctds_trimmed, plot)
```

## Transect out

Make a section of mainline stations

```{r}
section <- ctds_trimmed[c(1:6,8)] |> 
  as.section()

section
```

Basic Plot

```{r}
section |> plot()
```

Interpolated plot with bathymetry

```{r}
t <- download.topo(west = -72.5, east = -69, north = 41, south = 39.5) |> 
  read.topo()

section |> 
  plot(which = c("map", "temperature", "salinity", "oxygen"), ztype = "image", showBottom = t, showStations = TRUE)
```

## Transect in

Make a section of mainline stations

```{r}
section <- ctds_trimmed[41:54] |> 
  as.section()

section
```

Basic Plot

```{r}
section |> plot()
```

Interpolated plot with bathymetry

```{r}
t <- download.topo(west = -72.5, east = -69, north = 41, south = 39.5) |> 
  read.topo()

section |> 
  plot(which = c("map", "temperature", "salinity", "oxygen"), ztype = "image", showBottom = TRUE, showStations = TRUE)
```

